---
title: "Python code chunks in R Markdown"
date: 2018-02-22
---

> https://github.com/yihui/knitr-examples/blob/master/023-engine-python.Rmd

## A normal R code chunk

```{r}
library(reticulate)
# Sys.setenv(RETICULATE_PYTHON = "/home/czg/.virtualenvs/vsc/bin/python")
x <- 42
print(x)
# import matplotlib as mat
```

## Modify an R variable

In the following chunk, the value of `x` on the right hand side
is `r x`, which was defined in the previous chunk.

```{r}
x <- x + 12
print(x)
```

## A Python chunk

This works fine and as expected. 

```{python}
x = 42 * 2
print(x) 
```

The value of `x` in the Python session is `r py$x`.
It is not the same `x` as the one in R.

## Modify a Python variable

```{python}
x = x + 18 
print(x)
```

Retrieve the value of `x` from the Python session again:

```{r}
py$x
```

Assign to a variable in the Python session from R:

```{r}
py$y <- 1:5
```

See the value of `y` in the Python session:

```{python}
print(y)
```

## Python graphics

You can draw plots using the **matplotlib** package in Python.

```{r, engine='python'}
import matplotlib.pyplot as plt
plt.plot([0, 2, 1, 4])
plt.show()

import sys  
for p in sys.path: 
    print(p)

```